{\it E}nKCF: Ensemble of Kernelized Correlation Filters for High-Speed, Object Tracking

### 2017-08-04 wacv_for_review.tex
Deep features figure added

Our {\it E}nKCF framework provides us flexibility to exploit different feature representations. The translation filters, $R_{t}^{L}$ and $R_{t}^{S}$, 
considers at more than twice larger area than $R_{s}$. Taking this into account, we can assign deeper feature encodings to $R_{s}$ as it requires less
spatial information than  $R_{t}^{L}$ and $R_{t}^{S}$. Hence, we assign the activations of the fourth convolutional layer features ($26\times26\times128$) to $R_{s}$  whereas $R_{t}^{L}$ and $R_{t}^{S}$ are assigned the activations of the second layer features ($109\times109\times64$). This feature assignment is represented as  \textit{conv224-VGG}. Additionally, we assign the second convolutional layer features to $R_{s}$ as in $R_{t}^{L}$ and $R_{t}^{S}$ and compare this setting  (\textit{conv222-VGG}) to  \textit{conv224-VGG}. We use the VGGNet as it provides higher spatial resolution at the first layers than than AlexNet \cite{krizhevsky2012imagenet}.

@@

\begin{figure}[h]
\begin{tabular}{ccc}
\tiny\quad\quad\quad\textbf{UAV123}\\
\includegraphics[width=3.30cm]{./figures/pr_deep.eps}
\includegraphics[width=3.50cm]{./figures/sr_deep.eps}\\
\end{tabular}
\caption{Comparison of {\it E}nKCF's performance with deep features and HoG and Color features.}
\label{fig:UAV123_DATASET_DeepFeatures}
\end{figure}

>>>>

Our {\it E}nKCF framework provides us flexibility to exploit different feature representations. The translation filters, $R_{t}^{L}$ and $R_{t}^{S}$, 
considers at more than twice larger area than $R_{s}$. Taking this into account, we can assign deeper feature encodings to $R_{s}$ as it requires less
spatial information than  $R_{t}^{L}$ and $R_{t}^{S}$. Hence, we assign the activations of the fourth convolutional layer features ($26\times26\times128$) to $R_{s}$  whereas $R_{t}^{L}$ and $R_{t}^{S}$ are assigned the activations of the second layer features ($109\times109\times64$). This feature assignment is represented as  \textit{conv224-VGG} and shown in fig.~\ref{fig:Filters_CNN}. Additionally, we assign the second convolutional layer features to $R_{s}$ as in $R_{t}^{L}$ and $R_{t}^{S}$ and compare this setting  (\textit{conv222-VGG}) to  \textit{conv224-VGG}. We use the VGGNet as it provides higher spatial resolution at the first layers than than AlexNet \cite{krizhevsky2012imagenet}.

@@

\begin{figure}[!h]
\centering
\includegraphics[width=0.48\textwidth]{./figures/Filters_Details_CNN.pdf}
\caption{The proposed conv224-VGGNet feature extraction framework to use deep features in {\it E}nKCF. $R_{t}^{L}$ and $R_{t}^{s}$ are applied Hanning Window
to avoid distortion due to FFT operation whereas $R_{s}$ is not applied as it would result in target information loss.}
\label{fig:Filters_CNN}
\end{figure}

\begin{figure}[t]
\begin{tabular}{ccc}
\tiny\quad\quad\quad\textbf{UAV123}\\
\includegraphics[width=3.30cm]{./figures/pr_deep.eps}
\includegraphics[width=3.50cm]{./figures/sr_deep.eps}\\
\end{tabular}
\caption{Comparison of {\it E}nKCF's performance with deep features and HoG and Color features.}
\label{fig:UAV123_DATASET_DeepFeatures}
\end{figure}
